### 2016-04-29 ch01-intro/introduction.tex
Some work on introduction

\section{System idenfication}
\subsection{Linear System theory}
\subsection{System Identification Approaches}

@@

\section{Publications}
   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.

@@

The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
\begin{itemize}
  \item \fullcite{Lumori2014TIM}.
\end{itemize}
Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
\begin{itemize}
    \item \fullcite{Verbeke2015Benelux}.
\end{itemize}

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and 
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015SYSID}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}

>>>>

\section{System idenfication}

\subsection{Linear System theory}
\subsection{System Identification Approaches}

@@

For seasoned identification practitioners, methods that require little interaction are an opportunity for automation.
This is especially important for complex systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, \ldots
For such complex systems, building a model can be time-consuming and laborious if one has to supervise every step of the process.
For more advanced users, user-friendly methods can hence allow to deal with more complex systems in a shorter amount of time such that the economical cost of building a model is reduced.

In this dissertation, the focus lies on \gls{LTI} systems.
While this might seem as a very restrictive choice, this is one of the fundamental settings for system identification.
In particular, \gls{LTI} systems are a first step for many people to build a system model.
In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
When such a linear model is not adequate, a more flexible model, e.g. a time-varying model, a nonlinear model or parameter-varying model needs to be constructed.
However, many of those advanced modeling approaches build upon \gls{LTI} models.
As such, improvements in estimating \gls{LTI} models also indirectly benefit more advanced models.

\section{Outline and Publications}
   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.

@@

The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished manuscript.
 The so-called time-truncated \gls{LPM} that is presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
\begin{itemize}
  \item \fullcite{Lumori2014TIM}.
\end{itemize}
In particular, this smoother enables one to reduce the effect of noise on an estimated \gls{FRF} using an automated approach.
Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
\begin{itemize}
    \item \fullcite{Verbeke2015Benelux}.
\end{itemize}

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and the 2014 Leuven Conference on Noise and Vibration Engineering (ISMA) in Leuven:
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
Experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015SYSID}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}
